Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-08 longSC.tex
few minor changes

\begin{figure*}[!]
            \begin{center}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_EKRT.eps}}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_EKRT.eps}}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_EKRT.eps}}
              \end{center}
        \caption{Measurements of  SC(5,2) (a), SC(5,3) (b) and SC(4,3) (c) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}}        \label{fig:Figure_5}
\end{figure*}

@@

\begin{figure*}[!]
	\begin{center}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}. Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers. The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines. Upper panels are the results of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
        \label{fig:Figure_6}
        \end{center}   
 \end{figure*}

 \begin{figure*}[!]
	\begin{center}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$.}
        \label{fig:Figure_7}
        \end{center}   
 \end{figure*}

@@

We list here the important findings from the model comparisons:
\begin{enumerate}[(i)]
	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data qualitatively but it cannot describe the data quantitively for most of the centrality ranges.
	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations.
	\item The sign of NSC(3,2) in 0-10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce the sign.
	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most of the centrality ranges while the string melting AMPT model fails to describe them.
	%\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors. This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.

>>>>

\begin{figure*}[!]
            \begin{center}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_EKRT.eps}}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_EKRT.eps}}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_EKRT.eps}}
              \end{center}
        \caption{Measurements of  SC(5,2) (a), SC(5,3) (b) and SC(4,3) (c) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}        
        \label{fig:Figure_5}
\end{figure*}

@@

\begin{figure*}[!]
	\begin{center}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}. Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers. The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
        \label{fig:Figure_6}
        \end{center}   
 \end{figure*}

 \begin{figure*}[!]
	\begin{center}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
        \label{fig:Figure_7}
        \end{center}   
 \end{figure*}

@@

We list here the important findings from the model comparisons:
\begin{enumerate}[(i)]
	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data qualitatively but it cannot describe the data quantitively for most of the centrality ranges.
	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations.
	\item The sign of NSC(3,2) in 0-10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce the sign.
	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
	%\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors. This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.
